Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-13 ieee_paper.tex
adding proper sections and labels

In Section~\ref{} we present the computation of RBFs and how it can be
expressed 16 multiplication of 4 vectors by 4 matrices. Section~\ref{}
presents an estimation of the instruction intensity of various form of
the computations and we show that a 5- to 6- fold improvement can be
expected when computing the 16 multiplications simultaneously and
reach a total of about 200 Gflop/s. This performance represents
approximatively 10\% of the available flop/s of a Knight Corner
coprocessor. Therefore, it is necessary to have implementations that
perform the computation in as little amount of instructions as
possible. We describe in Section~\ref{} the details of the MIC
architecture and how to use specialized load, store, swizzle and
permutation instruction to efficiently bring the data in the vector
registers to be processed. Section~\ref{} gives some experimental
result about the amount of bandwidth that can be achieved depending on
how the spmv kernel is written and the actual performance of the
various kernel on multiple classes of matrices some generated for
analysis purpose and some extracted from and RBF
application. Concluding remarks and perspectives are provided in
Section~\ref{}.

\section{Derivatives of Radial Basis Functions}

@@

\section{Conclusion}
The conclusion goes here. this is more of the conclusion

>>>>

In Section~\ref{sec:rbf} we present the computation of RBFs and how it
can be expressed 16 multiplication of 4 vectors by 4
matrices. Section~\ref{sec:model} presents an estimation of the
instruction intensity of various form of the computations and we show
that a 5- to 6- fold improvement can be expected when computing the 16
multiplications simultaneously and reach a total of about 200
Gflop/s. This performance represents approximatively 10\% of the
available flop/s of a Knight Corner coprocessor. Therefore, it is
necessary to have implementations that perform the computation in as
little amount of instructions as possible. We describe in
Section~\ref{sec:imple} the details of the MIC architecture and how to
use specialized load, store, swizzle and permutation instruction to
efficiently bring the data in the vector registers to be
processed. Section~\ref{sec:expe} gives some experimental result about
the amount of bandwidth that can be achieved depending on how the spmv
kernel is written and the actual performance of the various kernel on
multiple classes of matrices some generated for analysis purpose and
some extracted from and RBF application. A performance of xxx GFlop/s
is achieved on real scenario. Concluding remarks and perspectives are
provided in Section~\ref{sec:ccl}.

\section{Derivatives of Radial Basis Functions}
\label{sec:rbf}

\section{Modelization of the Potential Improvements}
\label{sec:model}

\section{Efficient Implementation on the Intel Xeon Phi processor}
\label{sec:impl}

\section{Experimental Validation}
\label{sec:expe}

@@

\section{Conclusions and Perspectives}
\label{sec:ccl}

The conclusion goes here. this is more of the conclusion
